\section*{Hobbies / Side projects}
\subsection*{Books}

Some of the books that were fundamental for my career (in temporal order):

\begin{itemize}
    \item
        \textit{Refactoring: Improving the Design of Existing Code}.
        Martin Fowler.
    \item
        \textit{The Design of the UNIX Operating System}.
        Maurice J. Bach.
    \item
        \textit{Structure and Interpretation of Computer Programs}.
        Harold Abelson, Gerald Jay Sussman, Julie Sussman.
    \item
        \textit{Test Driven Development for Embedded C}.
        James W. Grenning.
    \item
        \textit{Effective Modern C++}.
        Scott Meyers.
    \item
        \textit{The Linux Programming Interface}.
        Michale Kerrisk.
    \item
        \textit{Heterogeneous Computing with OpenCL}.
        Benedict Gaster, Lee Howes, David R. Kaeli, Perhaad Mistry, Dana Schaa
\end{itemize}

\subsection*{Technology}

\begin{itemize}
    \item
        LineageOS (FLOSS operating system based on Android) on mobile devices.
    \item Raspberry Pi file server.
\end{itemize}

\subsection*{Talks}

Presentations and source files at \url{https://bbguimaraes.com/talks}.

\begin{itemize}
    \item
        \begin{description}
            \item[Title]: Linux containers
            \item[Events]:
                ContainerCon Europe (2016), FISL (2015), TcheLinux Porto Alegre
                (2014), pycaxias (2014)
            \item[Summary]:
                A presentation of the tools in the kernel and userspace for
                application isolation. Technologies in constant development
                will be discussed: systemd, lxd and docker, with practical
                demonstrations of their use in systems development and
                discussion of their advantages and disadvantages.
            \item[Websites]:
                \begin{itemize}
                    \item \url{https://linuxconcontainerconeurope2016.sched.com/event/7oHa}
                    \item \url{http://schedule.fisl16.softwarelivre.org/#/talk/447}
                    \item \url{http://poa.tchelinux.org/#speech-12}
                    \item \url{http://pycaxias.org/2015/index.html#speech-3}
                \end{itemize}
        \end{description}
    \item
        \begin{description}
            \item[Title]: Free cloud with owncloud
            \item[Event]: TchêLinux Caxias (2014)
            \item[Summary]:
                A presentation of the project and a practical guide to enable
                people with little or no experience with servers and/or
                owncloud to install and configure this personal cloud service.
            \item[Website]: \url{http://caxias.tchelinux.org#speech-4}
        \end{description}
    \item
        \begin{description}
            \item[Title]: bash and gnu/linux
            \item[Event]: TchêLinux Caxias (2013)
            \item[Summary]:
                A pratical demonstration of how the gnu tools in a linux
                operating system can be used in common day-to-day tasks of
                programmers/system administrators.
            \item[Website]:
                \url{http://tchelinux.org/wiki/evento_2013_08_cxs#bash_e_gnulinux}
        \end{description}
\end{itemize}

\subsection*{Research projects}

\begin{itemize}
    \item
        \begin{description}
            \item[Title]:
                Efficient liver surgery planning in 3D based on functional
                segment classification and volumetric information
            \item[Period]: 2010 (6 months)
            \item[Institution]: Universidade de Caxias do Sul / FAPERGS
            \item[Description]:
                development of a mass-spring system to simulate the thread of a
                surgical suture on a computer model of a human liver.
            \item[Technologies]:
                \begin{itemize}
                    \item \textbf{Operating systems}: linux, windows
                    \item \textbf{Languages/libraries}: c/c++, opengl
                    \item \textbf{Area}: graphics programming, physics
                \end{itemize}
        \end{description}
    \item
    \begin{description}
        \item[Title]: Development of an anti-phishing filter
        \item[Period]: 2011 (9 months)
        \item[Institution]: Universidade de Caxias do Sul / CNPq
        \item[Attributions]:
            integration of an anti-phishing filter based on artificial immune
            systems with the postfix mail server.
        \item[Technologies]:
            \begin{itemize}
                \item \textbf{Operating system}: linux
                \item \textbf{Languages}: shell, c\#
                \item \textbf{Programs}: postfix
                \item \textbf{Areas}:
                    systems programming, artificial intelligence
            \end{itemize}
    \end{description}
\end{itemize}

\subsection*{Music}

\begin{itemize}
    \item Music studies from the age of fifteen.
    \item
        Instruments: bass guitar, piano, guitar, mandolin, harmonica, drums, …
    \item
        Recording performances and publishing videos/scores/sources:
        \url{https://bbguimaraes.com/music}.
    \item
        Playing in bands, with one CD recorded:
        \url{https://www.youtube.com/larajackpot}.
\end{itemize}

\subsection*{Languages}

\begin{itemize}
    \item fluent: Portuguese, English
    \item familiarity: Italian, Spanish
    \item studying: Latin
\end{itemize}
