\section*{Personal projects}

I am fascinated by programming languages (C\slash++, Lua\slash Python,
assembler), computer architecture and operating systems, automated testing,
graphics and physics simulation, and heterogeneous computing.  Here are some of
my personal projects, where I strive to create software which is:

\begin{itemize}
    \item
        portable (x86\slash ARM, POSIX\slash Wasm\slash Windows)
    \item
        documented (Doxygen), tested (strict warnings, sanitizers, QTest unit
        tests, integration tests)
    \item easily built\slash distributed (Make, Autoconf, premake)
\end{itemize}

More at \url{https://gitlab.bbguimaraes.com}.

\vspace{0.25\baselineskip}

\href{https://bbguimaraes.com/nngn}{\texttt{nngn}}
--- 2D\slash 3D graphics\slash physics\slash audio\slash game engine
\begin{itemize}
    \item
        \href
            {https://bbguimaraes.com/nngn/docs/dir_68267d1309a1af8e8297ef4c3efbcdba.html}
            {C++20},
        \href
            {https://bbguimaraes.com/nngn/docs/dir_eb2a6c909ccee19b40dc174b15a80916.html}
            {Lua},
        Rust.
        Independent TUI / GUI (Qt)
        \href
            {https://bbguimaraes.com/nngn/docs/dir_4eeb864c4eec08c7d6b9d3b0352cfdde.html}
            {tools},
        \href
            {https://bbguimaraes.com/nngn/nngn.html?argv=demos/demo1.lua}
            {WebAssembly build}.
    \item
        \href
            {https://bbguimaraes.com/nngn/docs/dir_560415a5d2bc4999842279f4fc1debef.html}
            {Graphics}:
        Vulkan, OpenGL\slash ES, ASCII rasterizer.  Dynamic lights\slash
        shadows, post-processing, HDR.
    \item
        \href
            {https://bbguimaraes.com/nngn/docs/dir_e10d8d1736f2f8a793a6d4fd13649885.html}
            {Compute}:
        OpenCL compute back end, CPU\slash OpenCL collision detection,
        particle simulation.
\end{itemize}

\href{https://bbguimaraes.com/gdb_lua}{\texttt{gdb\_lua}}
--- GDB commands for embedded Lua
\begin{itemize}
    \item
        Statically-typed Python using the GDB Python API, support for
        multiple Lua versions at runtime.
    \item
        Data\slash call stack inspection, debugging data, pretty printers,
        recursive expansion of tables\slash structures.
\end{itemize}

\href{https://bbguimaraes.com/machinatrix}{\texttt{machinatrix}}
--- chat robot for the Matrix decentralized communication protocol
\begin{itemize}
    \item
        C11, POSIX networking, SQLite, \texttt{libcurl}, \texttt{tidy},
        \texttt{cjson}, layered architecture, privilege separation.
\end{itemize}

\href{https://bbguimaraes.com}{\texttt{bbguimaraes.com}}
--- personal website
\begin{itemize}
    \item
        \href{https://bbguimaraes.com}{static},
        \href{https://git.bbguimaraes.com}{git},
        \href{https://gitlab.bbguimaraes.com}{gitlab},
        \href{https://matrix.bbguimaraes.com}{matrix},
        \href{https://nextcloud.bbguimaraes.com}{nextcloud},
        \href{https://mastodon.bbguimaraes.com}{mastodon}
    \item built\slash deployed using Linux containers
\end{itemize}

\href{https://bbguimaraes.com/codex}{\texttt{codex}}
--- code experiments, research notes
\begin{itemize}
    \item
        \texttt{cpp.lua}: C preprocessor which outputs detailed information
        about macro expansion.
\end{itemize}

\href{https://bbguimaraes.com/impero}{\texttt{impero}}
--- graphical command executor (C++20, Qt)

\href
    {https://gitlab.bbguimaraes.com/bbguimaraes/dotfiles.git}
    {\texttt{dotfiles}}
--- scripts, \texttt{ansible} PC\slash server configuration
